---
name: Nicole
surname: Brewer
position: "Research Software Engineer | Graduate Research Assistant"
address: "Arizona State University, Tempe, AZ"
#phone: +1 22 3333 4444
www: nicole-brewer.com
mastodon: "\\@catch_me_coding\\@fosstodon.org"
twitter: catch_me_coding
github: nicole-brewer
linkedin: nicole-brewer
date: "`r format(Sys.time(), '%B %Y')`"
output:
  vitae::awesomecv:
    keep_tex: true
headcolor: '000000'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tibble)
library(dplyr)
```

# Education

```{r}
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "PhD Computational History and Philosophy of Science", "Expected May 2027", "Arizona State University", "Tempe, AZ",
  "BS Mathematics with Computer Science", "December 2018", "Purdue Univeristy", "West Lafayette, IN",
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```

# Publications

```{r}
# sort entries by date issued
bibliography_entries("combined.bib") %>%
  arrange(desc(issued))
```

# Honors and Awards

```{r}
tribble(
  ~Year, ~Desc, ~Title, ~Awarder,
  '2022', '', '\\textbf{Outstanding Mentorship Award} (\\$750), ASU Graduate and Professional Student Association', '',
  '2022', '', '\\textbf{GPSA Individual Travel Award} (\\$950), ASU Graduate and Professional Student Association', '',
  #'2022', '', '\\textbf{eScience Travel Grant} (\\$700), National Science Foundation', '',
  '2021', "Travel support for early career scholars who are considering pursuing philosophy of science", '\\textbf{UPSS Delegate} (\\$500), Philosophy of Science Biennial Meeting', '',
  '2020', "Honorarium awarded for notable achievement in the advancement of science gateways", '\\textbf{Young Professional of the Year Award} (\\$500), Science Gateways Community Institute', '',
  #'2018', 'Travel support to attend PEARC18 and participate in the student program', '\\textbf{Travel Grant} (\\$500), XSEDE', '',
  '2018', 'Awarded for "Classification of Periodicity in Subtraction Game Sequences"', '\\textbf{Phil Andrews Award for Most Transformative Contribution}, Practice and Experience in Advanced Research Computing Conference', ''
) %>% 
  brief_entries(what=Title, when=Year, with=Awarder, .protect = FALSE)
```

# Grants and Fellowships

```{r}
# if no url, use \\newline
tribble(
 ~ title, ~ role, ~ amount, ~ funder, ~ date,
 'Better Scientific Software Fellowship', 'Awardee', '\\$25,000', 'Exascale Computing Project (DOE/NSF)', 'Jan 2023',
 'School of Life Science Fellowship', 'Awardee', '\\$2,500', 'Arizona State University', 'Aug 2022',
)  %>% 
   brief_entries(glue::glue('\\textbf{<title>} (<amount>), <funder>, <role>.', .open = "<", .close = ">"), date, .protect = FALSE)
```

# Posters and Presentations
```{r}
tribble( 
 ~ title, ~ format, ~ event, ~ place, ~ date, ~ url, ~ additional,
    'Standalone Web Application Template', 'presenter', 'Mini Gateways 2022', 'Virtual', 'Mar 2022','https://youtu.be/iv6KswTyVLE?t=4086', '',
   'Scientific Web Applications with Jupyter Notebooks', 'presenter', 'US-RSE Comm. Call', 'Virtual', 'Mar 2022','https://doi.org/10.5281/zenodo.6345262', '',
 "Leveraging Traits for Highly Interactive Computational Tools in Jupyter", 'abstract', "Gateways 2021", "Virtual", 'July 2021','https://doi.org/10.5281/zenodo.5570605', 
 ' (\\underline{\\href{https://www.youtube.com/watch?v=O_KAupUYcyk}{video}})',
 "Classification of Periodicity in Subtraction Game Sequences", "poster", "PEARC18", "Pittsburg, PA", 'June 2018', 'https://doi.org/10.5281/zenodo.7133317', '',
 ) %>% 
  brief_entries(glue::glue('\\textbf{<title>} (\\underline{\\href{<url>}{<format>}}) <additional>', .open = "<", .close = ">"), date, event, .protect = FALSE)
```

<!-- # Peer-Reviewed Notebooks and Scientific Web Applications -->

# Professional Experience
```{r}
tribble(
  ~ Job, ~ Year, ~ Institution, ~ Where, ~Desc,
  "Research Software Engineer", "Feb 2019 - Apr 2022", "ITaP Research Computing", "Purdue University", list('Implemented a highly interactive, Jupyter-based, GUI wrapper for power analysis software in order to expand \\newline the audience and ease of use of a rich set of computational functions via a user-friendly interface', 
  'Facilitated software design, the implementation of best practices, and internal tool development, and lab \\newline documentation to improve the overall sustainability of lab software',
  'Transform disparate data acquisition and processing scripts into modular classes to be reused for scientific workflows'),
  'Software Verification Engineer', 'Nov 2017 – Nov 2018', 'Aptiv', 'West Lafayette, IN',
  list('Developed comprehensive Unit Test projects that utilized CAN bus protocol communications to verify \\newline automotive controller hardware'), 
) %>% 
  detailed_entries(Job, Year, Institution, Where, Desc)
  # 'Designed a dynamic Solr schema to index and query layered geospacial and user-defined metadata', 
  #'Implemented interactions with this database in a web application in PHP and JavaScript',
  #'Mentored students participating in semester-long internships'
```


# Research Experience
```{r}
tribble(
  ~Year, ~Type, ~Institution, ~Desc,
  'Aug 2022 - Present', 'Graduate Research Assistant', 'Complex Adaptive Systems, Arizona State University', list('Advisor: Manfred Laubichler',
  'Using natural language processing, machine learning, network analysis, high performance computing, and mixed \\newline social science methods to model the evolution of scientific standards through time', 'Documenting and adapting code and data from prior projects for reuse'),
  'June 2018 - Dec 2018', 'Student Cluster Competition, Reproducibility Challenge', 'Research Computing, Purdue University', list(
    'Advisors: Betsy Hillery', 'Built a small cluster and applied optimization techniques in a non-stop, 48-hour challenge at the SC18 conference', 'Compiled a scienfitic application from an accepted paper from the prior year’s Technical Program and interacted \\newline directly with the paper’s authors to reproduce specific results and conclusions from the paper'),
    'Jan 2016 - June 2017', 'CSoI Channels Scholar REU',"Center for Science of Information, NSF STC", 
  list('Advisor: Mark Daniel Ward', 
       'Utilized HPC clusters to efficiently create large data sets pertaining to combinatorial game theory',
       'Analyzed batching strategies of parallel computation to efficiently detect an unknown length of repeating sequences in long strings',
       'Developed a command line interface and file managment system in Python to prevent human error and enhance the usability of codebase'),
) %>% 
  detailed_entries(what=Institution, when=Year, with=Type, why=Desc)
```

# Conference Activity
```{r}
tribble(
  ~Activity, ~Role, ~Conference, ~Location, ~When, ~Link,
  'Notebook Submission Subcommittee', 'Co-Chair', 'US-RSE Conference', 'Chicago, IL', 'Oct 2023', '',
  'Student Program', 'Co-Chair', 'US-RSE Conference', 'Chicago, IL', 'Oct 2023', '',
 'Reproducibility Challenge', 'Committee Member', 'SC22', 'Dallas, TX',  'Nov 2022', '', 
   "Software Engineering Topics Relevant to eScience", "Invited Panelist", "eScience22", "Salt Lake City, UT", "Oct 2022", '', #"https://us-rse.org/rse-escience-2022/abstracts", 
  "How to Recruit and Sustain a Diverse and Inclusive Workforce",  "Invited Panelist", "Int'l RSE Day", "Virtual", "Oct 2021", '(\\underline{\\href{https://doi.org/10.5281/zenodo.7133472}{slides}})',
) %>% 
  brief_entries(glue::glue('\\textbf{<Role>}, <Activity>, <Conference>. <Link>', .open = "<", .close = ">"), When, .protect = FALSE)
```

# Professional Service
```{r}
tribble(
  ~Date, ~Position, ~Group, ~Institution, ~Desc,
  'Jan 2022 - Present', 'Council Member', 'International Council of RSE Association', "International", 
  c('Chaired and organized council meetings', 'Participated in coordinated efforts, such as conferences, workshops, and podcast episodes, that fostered international collaboration'),
  'Jan 2022 - Present', 'Steering Committee Member', 'Research Software Engineering Association', 'United States',
  c('Committed at least five hours per week to steering committee and other meetings including the Diversity, Equity, \\newline and Inclusion (DEI), Outreach, and Code of Conduct and Moderation working groups', 'Established the DEI Speaker Series and DEI Media Meetings.'),
   'Jan 2020 - May 2022', "Co-Chair", 'Women in High Performance Computing', 'Purdue University', 
  c('Organized and served as the host for invited talks where members shared their work or research', 'Created and maintained a formal newsletter featuring opportunities and events for members', 'Submitted annual reports and participated in conference events for the international umberella orgainzation')
    #'Established the \\href{https://www.nicole-brewer.com/long-tales-of-science/}{Long Tales of Science podcast} to continute to improve visibility of women in HPC in spite of discontinuing in-person events in the wake of the COVID-19 pandemic')
) %>% 
  detailed_entries(what=Group, when=Date, with=Position, where=Institution, why=Desc, .protect = FALSE)
```

\medskip
## Reviewing

```{r} 
  tribble(
  ~Date, ~Role, ~Program,
  '2023', 'Reviewer', 'Notebook Submissions, US-RSE Conference',
  '2022', 'Reviewer', 'Reproducibility Paper, Student Cluster Competition, SC22', 
) %>% 
   brief_entries(glue::glue('\\textbf{<Role>}, <Program>', .open = "<", .close = ">"), Date, .protect = FALSE)
```

# Certifications and Training

```{r}
tribble(
  ~Date, ~Position, ~Title, ~Institution, ~Desc,
   "May 2020", 'SDSC Summer Institute', 'San Diego Supercomputer Center', 'Virtual', 
  'Machine learning in R, big data with Spark, parallel programming with Python, and scientific visualization',
  'July 2019', 'Applied Management Principles', 'Krannert Executive Education', 'Purdue University', c('Purdue\'s "mini-MBA" covering accounting, finance, strategy, marketing, negotiations & problem solving, and entrepreneurial skills essential to effective laboratory and research project managment')
) %>% 
  detailed_entries(what=Title, when=Date, with=Position, where=Institution, why=Desc)
```


# Teaching Experience
```{r}
tribble(
  ~Date, ~Position, ~Title, ~Institution, ~Desc,
  #'Aug 2022 - Dec 2022', 'Curriculum Developer', 'Graduate Partners in Science Education: K - 12 STEM Education & Outreach', 'Arizona State University', 
  #c('created an interactive lesson about parallel and distributed computing and modified existing lessons for remote instruction', 'learned teaching practices that are engaging and inclusive'), 
   "Aug 2015 - May 2016", 'Undergraduate Teaching Assistant', 'Object-Oriented Programming', 'Purdue Univeristy', 'Taught object oriented programming in Java, debugging In Intellij, JUnit Testing, and app development in Android Studio in laboratory',
) %>% 
  detailed_entries(what=Position, when=Date, with=Title, where=Institution)
```

\medskip

<!-- Add "peer reviewed" -->
## Open Source Education and Training Materials
```{r}
# if no url, use \\newline
tribble( 
 ~ title, ~ type, ~ year, ~url,
 'HPC Unplugged: A lesson plan for teaching parallel and distributed computing', 'booklet', 'Sep 2022', 'https://www.nicole-brewer.com/hpc-unplugged/',
 "R for Research Scientists", "booklet", 'Mar 2020', 'https://www.nicole-brewer.com/r-for-research-scientists/'
 ) %>% 
  brief_entries(glue::glue('\\textbf{<title>} (\\underline{\\href{<url>}{<type>}})', .open = "<", .close = ">"), year, .protect = FALSE)
```

# Mentorship and Outreach
```{r}
  tribble(
  ~Date, ~Position, ~Group, ~Institution, ~Desc,
  'Oct - Nov 2022', 'Mentor', 'Mentor–Protégé Matching', 'SC22',
  'Provided career and educational advise and helped extend the professional network of an undergraduate mentee \\newline at the Supercomputing conference',
  'Aug - Nov 2019', 'Staff Advisor', 'Student Cluster Competition', 'SC19', 
  'Mentored students taking a weekly, two credit hour course in preparation for a competition that I had participated in \\newline the year prior', 
  'June 2019', 'Mentor', 'Science Gateways Community Institute Hackathon', 'PEARC19' ,
  'Answered students code-related questions over the course of an intensive, three day conference hackathon',
  'Aug 2018 - May 2019', 'Staff Mentor', 'Discover Park Undergraduate Research Internship', 'Purdue University', 
  'Defined the scope of a small project related to our ongoing research projects and met with each student bi-weekly \\newline during the course of the semester to help them set achievable short-term goals and guide \\newline them through roadblocks they encountered',
  'Aug - Dec 2018', 'Near-Peer Mentor', 'Mentors for Aspiring Girls in Computing', 'Purdue University', 'Led hands-on activities to teach computer science concepts to local middle and high school students in order to \\newline improve the recruitment and retention of young women in technology careers'
  ) %>% 
  detailed_entries(what=Position, when=Date, with=Group, where=Institution, why=Desc, .protect=FALSE)
```

# Science Communication and Broader Impacts
```{r}
# if no url, use \\newline
tribble(
 ~ title, ~ type, ~ event, ~ place, ~ date, ~ url, ~ format,
 'Reproducibility Initiative at SC22', 'Host', 'Long Tales of Science', 'Podcast', 'Mar 2023', 'https://nicole-brewer.github.io/long-tales-of-science/005/', 'episode',
 'Trial by Fire', 'Host', 'Long Tales of Science', 'Podcast' , 'May 2022',
 'https://nicole-brewer.github.io/long-tales-of-science/004/', 'episode',
  "Research Software Engineering", "Interviewee", "Hello PhD", "Podcast", "Apr 2022",
 'http://hellophd.com/2022/03/172-research-software-engineer/','episode',
 'A kind-of brief shared early history of US-RSE', 'Co-Author', 'US-RSE', 'Blog', 'Feb 2022',
 'https://us-rse.org/2022-02-06-a-brief-history-of-usrse/', 'post',
 'Call 1-800-HLP-DESK', 'Host', 'Long Tales of Science', 'Podcast', 'Dec 2021', 
 'https://nicole-brewer.github.io/long-tales-of-science/003/', 'epidode',
 'Models and Simulations Run on the Cluster and in the Family', 'Host', 'Long Tales of Science', 'Podcast', 'Oct 2020',
 'https://nicole-brewer.github.io/long-tales-of-science/002/', 'episode'
)  %>% 
   brief_entries(glue::glue('\\textbf{<type>}, <title>, \\textit{<event>}. (\\underline{\\href{<url>}{<format>}})', .open = "<", .close = ">"), date, .protect = FALSE)
```

# Extracurricular Leadership
```{r}
  tribble(
  ~Date, ~Position, ~Group,
  'Aug 2016', 'Vice President', 'Purdue University Triathlon Club', 
   'Aug 2015', 'Social Media Manager', 'Purdue University Triathlon Club', 
) %>% 
  brief_entries(glue::glue('\\textbf{<Position>}, <Group>', .open = "<", .close = ">"), Date, .protect = FALSE)
```

\newpage

# Extracurricular Activity
```{r}

tribble(
  ~BottomLeft, ~BottomRight, ~TopLeft, ~TopRight,
   'Private lessons from ASU faculty associate Cathy Bates', '', 'Music Theory and Piano Lessons', 'Jan 2023 - May 2023',
    'ASU Psychodelic Rock Band, RuQe', '', 'Vocalist and Keyboardist', 'Aug 2022 - Dec 2022'


) %>% 
  detailed_entries(what=BottomLeft, when=BottomRight, with=TopLeft, where=TopRight, .protect = FALSE)
```


## Major Endurance Sport Events
```{r} 
  tribble(
  ~Date, ~Event, ~Location,
  'Apr 2019', 'USA Triathlon Collegiate Club National Championships', 'Tempe, AZ',
  'Oct 2018', 'Chicago Marathon', 'Chicago, IL', 
  'Aug 2018', 'Ironman 70.3 Steelhead Triathlon', 'Benton Harbor, MI',
  'Aug 2017', 'Ironman 70.3 Steelhead Triathlon', 'Benton Harbor, MI',
  'Apr 2017', 'USA Triathlon Collegiate Club National Championships', 'Tuscaloosa, AL',
  'Nov 2016', 'Monumental Marathon', 'Indianapolis, IN',
  'Aug 2016', 'Ironman 70.3 Steelhead Triathlon', 'Benton Harbor, MI',
  'Apr 2016', 'USA Triathlon Collegiate Club National Championships', 'Clemson, SC',
  'Jan 2016', 'Disney World Marathon', 'Orlando, FL',
) %>% 
   brief_entries(glue::glue('\\textbf{<Event>}, <Location>', .open = "<", .close = ">"), Date, .protect = FALSE)
```

<!-- Skills 
Languages Python, R, PHP, JavaScript, Java, C, C#, HTML/CSS
Containers Docker, Kubernetes
Databases Solr, Elasticsearch, MongoDB
Platforms Linux (CentOS, RHEL, Ubuntu), MacOS, Windows
Development Tools Git, Vim, RStudio, IntelliJ, AndroidStudio, Visual Studio, SVN
-->
